Master Thesis

### 2013-06-26 gacg.tex
Fixing something...???
Fixed the assumptions in the decid. of G-ACGs

$$
\mathcal{I}_{\mathcal{G}}(v) = \{t \in \Lambda(\Sigma_v)
\mid\ \vdash_{\Sigma_v} t : S_v\}
$$
$$
\mathcal{E}_{\mathcal{G}}(v) = \mathcal{I}_{\mathcal{G}}(v) \cap
\bigcap_{(u,v) \in E} \mathcal{L}_{(u,v)}(\mathcal{E}_{\mathcal{G}}(u)).
$$

@@

Our intent here is to show that by extending the formalism we have not
made the problem of parsing more difficult, at least in terms of
decidability if not in terms of complexity. Let us therefore imagine a
graphical ACG where every edge (two signatures, distinguished types and
a lexicon) is an ACG for which there is an effective parsing algorithm
and type checking is decidable in all the signatures of the graphical
ACG. Then we can prove the existence of a simple effective parsing
algorithm for any of the extrinsic languages defined in the graphical
ACG.

>>>>

$$
\mathcal{I}_{\mathcal{G}}(v) = \{t \in \Lambda(\Sigma_v)
\mid\ \vdash_{\Sigma_v} t : S_v\}
$$
$$
\mathcal{E}_{\mathcal{G}}(v) = \mathcal{I}_{\mathcal{G}}(v) \cap
\bigcap_{(u,v) \in E} \mathcal{L}_{(u,v)}(\mathcal{E}_{\mathcal{G}}(u))
$$

@@

Our intent here is to show that by extending the formalism we have not
made the problem of parsing more difficult, at least in terms of
decidability if not in terms of complexity. Let us therefore imagine a
graphical ACG where every edge (two signatures, distinguished types and
a lexicon) is an ACG for which there is an effective parsing algorithm
that lets us find all the abstract terms for a given object term in
finite time and where type checking is decidable in all the signatures
of the graphical ACG. Then we can prove the existence of a simple
effective parsing algorithm for any of the extrinsic languages defined
in the graphical ACG.
